|

### 2020-03-03 analysis/paper/manuscript.Rmd
Change placement of new paragraph in the 'Towards open stock assessment' section

# Towards open stock-assessment

@@

The tools presented here are additions to the growing number of interactive stock assessment tools being developed and applied across the globe (see Appendix A). We believe that such tools represent an important a step forward in terms of open science and reproducible research in addition to being a major step forward in how stock assessments are presented and critiqued. Although these tools do not reveal the entire data pipeline, in conjunction with posting code and data on-line, they represent a significant advance over more traditional methods. Similarly, these tools do not fully alleviate pragmatic issues associated with reproducible research. For example, it is unlikely that an individual has the time to fully review and recreate a particular analysis in its entirety when most participants are already overcommitted [@banks2011].  Further, in the case of NCAM, considerable statistical experience and expertise is required simply to run the model. However, the dashboard approach removes many of these obstacles. The html file contains all model inputs, outputs and diagnostics in an open, and easy to use, interactive document that can be distributed prior to meetings.  As such, participants can assess the results and diagnostics at their leisure. Specific experience with the tools used to generate the results are not required to constructively and critically review of the results presented in the dashboard.

Pragmatic issues aside, it is not hard to picture a future whereby the full data to document pipeline is open and accessible. Open resources are actively being developed and used to improve accessibility to all the data, methods and results that feed into stock assessments [e.g. the Transparent Assessment Framework, https://taf.ices.dk/app/about; @magnusson2020]. Likewise, tools are being developed to facilitate the creation of reproducible advisory documents [e.g. @ices2018; @anderson2020; @regular2020]. These stand-alone advisory documents can be interactive, as is the case for the VISA tool [@ices2018] or, as discussed here, they can be supplemented by interactive tools. The technology behind these initiatives is rapidly developing and, at the same time, society is becoming increasingly reliant on screens. We may therefore reach a point where interactive documents become commonplace through increasingly open stock assessment processes.

>>>>

# Towards open stock assessment

@@

A culture of openness is actively evolving in the field of stock assessment and, at this point, it is not hard to picture a future where it is commonplace for the the full data to document pipeline to be open and accessible. Open resources are actively being developed and used to improve accessibility to all the data, methods and results that feed into stock assessments [e.g. the Transparent Assessment Framework, https://taf.ices.dk/app/about; @magnusson2020]. Likewise, tools are being developed to facilitate the creation of reproducible advisory documents [e.g. @ices2018; @anderson2020; @regular2020], and these documents can be interactive, as is the case for the VISA tool [@ices2018], or they can be supplemented by interactive tools. There is plenty of opportunity for synergies between these initiatives, as most are being developed using R, and all details and decisions can be traceable and accessible using an online repository such as GitHub. We therefore foresee a future where stock assessments become increasingly open and reproducible.

Providing open access to code and data, however, does not necessarily make a stock assessment more accessible. We believe that interactive tools, such as those presented here and in Appendix A, represent an important a step forward in terms of open science as they make the peer review process more efficient. Although these tools do not reveal the entire data pipeline, a wide range of peers can easily access and review details that may be inaccessible even if the pipeline is open. For example, it is unlikely that an individual has the time to fully review and recreate a particular analysis in its entirety when most participants are already overcommitted [@banks2011]. Further, in the case of NCAM, considerable statistical experience and expertise is required simply to run the model. However, the dashboard approach removes many of these obstacles. The html file contains all model inputs, outputs and diagnostics in an open, and easy to use, interactive document that can be distributed prior to meetings.  As such, participants can assess the results and diagnostics at their leisure. Specific experience with the tools used to generate the results are not required to constructively and critically review of the results presented in the dashboard.
